The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-22 paper.tex
update

 The temperature profile (left middle panel in \Cref{fig__profile}) along the positive z-axis in\
 \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
 the smooth region (purple band) emitting X-ray\
 is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

>>>>

 The temperature profile (left middle panel in \Cref{fig__profile}) along the positive z-axis in\
 \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
 the smooth region (purple band in \Cref{fig__profile}) emitting X-ray\
 is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.
